Canonical rings of log spin stacky curves

### 2015-07-08 curves-write-up/spin_cring.tex
fix typo in further q 2

\begin{question}
		\label{ques:fractional-weight}
			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
			where $K$ is the canonical divisor of $\sx$, can one bound the 
			degrees of generators and relations of $R_D$?
		\end{question}
		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
		gives an affirmative answer to this question: If $\sx$ has signature 
		$(g; e_1, \ldots, e_r; \delta)$ then $D$ is generated in degree at 
		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
		$2e$. 
		It may be possible to modify the proof of Lemma
		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
		weight modular forms. 
		Suitable generalizations of the 
		lemmas of Section ~\ref{sec:induction} might allow one to 
		follow similar questions to this paper and provide a general 
		answer to Question ~\ref{ques:fractional-weight}.

>>>>

\begin{question}
		\label{ques:fractional-weight}
			If $\sx$ is a stacky curve and $D \in \di \sx$ with $nD \sim K$, 
			where $K$ is the canonical divisor of $\sx$, can one bound the 
			degrees of generators and relations of $R_D$?
		\end{question}
		When $g=0$ and $D$ is effective, inductively applying Lemma ~\ref{lem:sat-1}  
		gives an affirmative answer to this question: If $\sx$ has signature 
		$(g; e_1, \ldots, e_r; \delta)$ then $R_D$ is generated in degree at 
		most $e = \max(e_1, \ldots, e_r)$ with relations in degree at most
		$2e$. 
		It may be possible to modify the proof of Lemma
		~\ref{lem:raise-stacky-order} to extend to the setting of fractional 
		weight modular forms. 
		Suitable generalizations of the 
		lemmas of Section ~\ref{sec:induction} might allow one to 
		follow similar questions to this paper and provide a general 
		answer to Question ~\ref{ques:fractional-weight}.
